A new tidy data structure to support exploration and modeling of temporal data

### 2019-11-22 tsibble.Rmd
minor tweaks

Since observational units are embedded, modeling and forecasting across units and time in a tsibble will be simplified. The tsibble key plays a role of the central transit hub in connecting multiple tables managed by the data, models, and forecasts. This neatly decouples the expensive data copy from downstream summaries, significantly reducing the storage space.

@@

In addition to the new verbs, the **dplyr** vocabulary has been adapted and expanded to facilitate temporal transformations. The **dplyr** suite showcases the general-purpose verbs for effectively manipulating tabular data. But these verbs need handling with care due to the context switch. A perceivable difference is summarizing variables between normal data and tsibble using `summarize()`. The former will reduce to a single summary, whereas the latter will obtain the index and their corresponding summaries.

@@

(ref:draw-qtl-cap) Small multiples of lines about departure delay against time of day, faceting day of week and 50%, 80% and 95% quantiles. A blue horizontal line indicates the 15-minute on-time standard to help grasp the delay severity. Passengers are apt to hold up around 18 during a day, and are recommended to travel early. The variations increase substantially as the upper tails.

>>>>

Since observational units are embedded, modeling and forecasting across units and time in a tsibble will be simplified. The tsibble key plays a role of the central transit hub in connecting multiple tables managed by the data, models, and forecasts. This neatly decouples the expensive data copying from downstream summarization, which can significantly reduce the required storage space.

@@

In addition to the new verbs, the **dplyr** vocabulary has been adapted and expanded to facilitate temporal transformations. The **dplyr** suite showcases the general-purpose verbs for effectively manipulating tabular data. But these verbs need handling with care due to the context switch. A perceivable difference is summarizing variables between normal data and tsibble using `summarize()`.The former gives a single summary for a data table, and the latter provides the corresponding summary for each index value.

@@

(ref:draw-qtl-cap) Line plots showing departure delay against time of day, faceted by day of week and 50%, 80% and 95% quantiles. The blue horizontal line indicates the 15-minute on-time standard to help grasp the delay severity. Passengers are more likely to experience delays around 18 during a day, and are recommended to travel early. The variations increase substantially as the upper tails.
